### 2021-06-28 rad-icfp-2021/purerad.tex
changing outline

\section{Efficient reverse-mode}
\label{sec:efficientrad}

@@

\begin{remark}
    One could rightfully wonder: where did reverse-mode really happened here?
    In a way, source UNF does not seem to do much. 
    Then $\Dsynrevsymbol$ is very simple on UNF.
    So perhaps everything happens when going from target UNF to target?
    \MH{finish or remove.}
\end{remark}

\subsection{Efficient representation}

\subsection{Optimisations via partial evaluation}

>>>>

\section{Simple pure reverse-mode differentiation}
\label{sec:simplediff}

\subsection{Source Language}

We consider a standard call-by-value language. 
It is a first-order language with array constructs and a few typical second-order array operations. 
The types !T1,T2! and terms !e1,e2! are in Figure~\ref{fig:source_grammar}.

\input{figures/source_grammar}

The typing rules are in Figure~\ref{fig:source_typesystem}. We have included a minimal set of array operations for the sake of illustration, 
but it is not difficult to add further operations. For scalar operations, we assume given a set of operations. 
!op1! and !op2! denote respectively unary and binary smooth operations on reals. 
We use infix notation for binary operators.
Typical examples include !cos, exp, +, *!. 
For the sake of simplicity in the development, the function in the array operations !map, map2, foldl! are quite restricted with and free variables. 
We also restrict to arrays of reals.
The general case is also useful and presented in Section~\ref{sec:generalisation}.

\input{figures/source_type_system}

@@

\subsection{Macro for pure reverse mode transformation} % (fold)
\label{sub:Macro for pure reverse mode transformation}

\subsection{Partial evaluation and optimisation} % (fold)
\label{sub:Partial evaluation and optimisation}

% subsectionPartial evaluation and optimisation (end)

### 2021-06-28 rad-icfp-2021/unf.tex
changing outline

\section{Simple reverse-mode differentiation}
\label{sec:simplediff}

\subsection{Source Language}

We consider a standard call-by-value language. 
It is a first-order language with array constructs and a few typical second-order array operations. 
The types !T1,T2! and terms !e1,e2! are in Figure~\ref{fig:source_grammar}.

\input{figures/source_grammar}

The typing rules are in Figure~\ref{fig:source_typesystem}. We have included a minimal set of array operations for the sake of illustration, 
but it is not difficult to add further operations. For scalar operations, we assume given a set of operations. 
!op1! and !op2! denote respectively unary and binary smooth operations on reals. 
We use infix notation for binary operators.
Typical examples include !cos, exp, +, *!. 
For the sake of simplicity in the development, the function in the array operations !map, map2, foldl! are quite restricted with and free variables. 
We also restrict to arrays of reals.
The general case is also useful and presented in Section~\ref{sec:generalisation}.

\input{figures/source_type_system}

\subsection{Source Unary Form}

@@

\subsection{Target Unary Form}

@@

\subsection{Macro for reverse mode}

@@

>>>>

\section{UNF}

\subsection{Source UNF} % (fold)
\label{sub:Source UNF}

@@

% subsubsectionSource UNF (end)

\subsection{Target UNF} % (fold)
\label{sub:Target UNF}

@@

\subsection{Simple reverse mode transformation} % (fold)
\label{sub:Simple reverse mode transformation}

@@

\subsection{transformations to and from UNF} % (fold)
\label{sub:transformations to and from UNF}

% subsection transformations to and from UNF (end)
